---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}
#Worst case is 3n vs n^2 when using prod(x)/x
#accounts for more 0s
f <- function(x) {
  #Get count of zeros if more than 1 return 0
  #for each x
  zeros = sum(x == 0)
  if (zeros > 1) 0 * x
  else if (zeros == 1) {
    #get total without accounting for 0
    #return 0 if our element isn't 0
    total = prod(x[x!=0])
    ifelse(x==0, total, 0)
  } else {
    #if no 0s, then do regular total/element
    total = prod(x)
    total/x
  }
}

x <- c( 1, 5, 2, 8) 
f(x)
```
    


## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers … except for: 
   multiples of 3 = “Fizz” 
   multiples of 5 = “Buzz”. 
   multiples of 3 and 5 = “FizzBuzz”
   
### Example

    > x <- 1:20
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz


### Solution

```{r}
f <- function(x) {
  # ...
  ifelse(x%%3 == 0, ifelse(x%%5 == 0, 'FizzBuzz','Fizz'), ifelse(x%%5 == 0, 'Buzz', x))
}
f(1:20)
```
